Digital Addiction

### 2024-02-15 paper/paper.qmd
import data

setwd("..")
#### Import Data ####
#### Explore ####
dinesafe_program_clean <-
  read_csv(
   here::here("scripts/02_data_cleaning.R"),
    show_col_types = FALSE
  )

>>>>

setwd("..")
#### Import Data ####
#### Explore ####
digital_clean_data <-
  read_csv(
   here::here("scripts/02_data_cleaning.R"),
    show_col_types = FALSE
  )
